R Notebook

### 2017-03-31 doc/RMD/MLG-distribution.Rmd
Add cool new version of graph

gcross           <- graph_from_data_frame(pop_graph, directed = FALSE)
E(gcross)$name   <- as.character(pop_graph$MLG)
E(gcross)$weight <- unchoose(table(E(gcross)$name)[E(gcross)$name])
colors <- viridis::magma(max(E(gcross)$weight) - 1, end = 0.8)
set.seed(50)
gcross %>%
  plot(., vertex.size = table(pop(clonecorrect(dat, ~Region)))[names(V(gcross))],
       edge.width = E(.)$weight - 1,
       layout = layout_as_star(., center = "MI"),
       # layout = layout_in_circle(.),
       edge.color = colors[E(.)$weight - 1])

@@

```{r, fig.width = 10, fig.height = 10}

pops <- crosses %>%
  group_by(Population) %>%
  summarize(MLG = list(as.character(MLG))) %>%
  group_by(Population) %>%
  mutate(interactions = list(pg$Population[pg$MLG %in% unlist(MLG)] %>% setNames(unlist(MLG)) %>% bind_rows(.id = "MLG") %>% distinct)) %>%
  mutate(graph = map(interactions, ~select(.x, from, to, MLG) %>% graph_from_data_frame(directed = FALSE)))
psize <- table(pop(clonecorrect(dat, ~Region)))
par(mfrow = c(3, 4))

@@

igraph::union(pops$graph[[1]], pops$graph[-1]) %>% 
  plot(., vertex.size = psize[names(V(.))],
       layout = layout_as_star(., center = "MI"))
```

>>>>

gcross           <- graph_from_data_frame(pop_graph, directed = FALSE)
E(gcross)$name   <- as.character(pop_graph$MLG)
E(gcross)$weight <- unchoose(table(E(gcross)$name)[E(gcross)$name])
colors <- viridis::magma(max(E(gcross)$weight) - 1, end = 0.8)
set.seed(500)
gcross %>%
  plot(., vertex.size = table(pop(clonecorrect(dat, ~Region)))[names(V(gcross))],
       edge.width = E(.)$weight - 1,
       layout = layout_as_star(., center = "MI"),
       # layout = layout_in_circle(.),
       edge.color = colors[E(.)$weight - 1])

@@

```{r, fig.width = 10, fig.height = 10}
psize <- table(pop(clonecorrect(dat, ~Region)))
pops <- crosses %>%
  mutate_if(is.factor, as.character) %>%
  group_by(Population) %>%
  summarize(MLG = list(as.character(MLG))) %>%
  group_by(Population) %>%
  mutate(size = psize[unlist(Population)]) %>%
  mutate(n_private = size - lengths(MLG)) %>%
  mutate(interactions = list(pg$Population[pg$MLG %in% unlist(MLG)] %>% 
                               setNames(unlist(MLG)) %>% 
                               bind_rows(.id = "MLG") %>% 
                               distinct() %>%
                               filter(Population == from | Population == to))) %>%
  mutate(graph = map(interactions, ~select(.x, from, to, MLG) %>% 
                       rename(name = MLG) %>% 
                       graph_from_data_frame(directed = FALSE)))
pops
par(mfrow = c(3, 4))

@@

gnew <- igraph::union(pops$graph[[1]], pops$graph[-1])

glayout <- layout_as_star(gnew, center = "MI")

glayout_df <- glayout %>% 
  data.frame %>% 
  setNames(c("x", "y")) %>% 
  as.list %>% 
  c(Population = list(names(V(gnew)))) %>% 
  dplyr::as_data_frame() %>%
  inner_join(pops)
V(gnew)$size <- glayout_df$size
V(gnew)$color <- viridis::viridis(100)[round(100 * (1 - glayout_df$n_private/glayout_df$size))]
gnew <- add_vertices(gnew, length(V(gnew)), size = glayout_df$n_private, color = "grey90")
glayout2 <- rbind(glayout, glayout)
plot(gnew, layout = glayout2)
